### 2018-07-05 Main.Rmd

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(igraph)
library(knitr)
library(lemon)
library(tibble)
```

>>>>

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2)
library(langcog) # useful things used by Language and Cognition Lab
library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(directlabels) # direct labeling of data in plots
library(stringr) # common string operations
library(lmtest) #  diagnostic checking in linear regression models
library(rwebppl) # interface to probabilistic programming language WebPPL
library(jsonlite) # JSON parser
library(nlme) # gaussian linear and nonlinear mixed-effects models
library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
library(HDInterval) # calculate highest density intervals of objects w/ pdf
library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
```
